%-------------------------
% Resume in Latex
% Author : Laksith Prabu
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\resumeItemBF}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \emph{#2} \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.05in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Laksith Prabu} \\ \vspace{5pt}
    \small +1 (510) 365-8851$|$ \href{mailto:laksith@berkeley.edu}{\underline{laksith@berkeley.edu}} $|$ \href{https://laksith.dev/}{\underline{laksith.dev/}} $|$
    \href{https://github.com/laksith19/}{\underline{github.com/laksith19/}}
\end{center}
\vspace{-17pt}


%-----------EDUCATION-----------
\section{Education}

\resumeSubHeadingListStart
    \resumeSubheading
        {University of California, Berkeley}{}{B.A. Computer Science}{May 2025}
        \resumeItemListStart
            \resumeItemBF{Relevant Coursework}{Data Structures \& Programming Methodology, Discrete Mathematics \& Probability Theory, Operating Systems \& System Programming, Computer Security, Designing Computer Science Education, Introduction to Artificial Intelligence, Introduction to Digital Design \& Integrated Circuits, Field-Programmable Gate Array Laboratory, Introduction to Software Engineering, Programming Languages \& Compilers }
        \resumeItemListEnd
        \resumeItemListStart
            \resumeItemBF{Organizations}{Open Computing Facility (OCF), Computer Science Mentors (CSM), The Algorithms \& Computing for Education (ACE) Lab}
        \resumeItemListEnd
\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}

\resumeSubHeadingListStart

\resumeSubheading
    {UC Berkeley EECS Department}{Berkeley, CA}{Lecturer}{June 2023 – August 2023}
    \resumeItemListStart
        \resumeItem{Delivered lectures, designed comprehensive lab excersices \& tests, and hired \& managed staff of 25+ TAs and Tutors for a class of 400+ students. Taught topics in Data Structures \& Algorithms using Java covering various topics including OOP \& Inheritance, Balanced Search Trees, Time \& Space Complexity, Hash Tables, Heaps, Graphs \& Search Algorithms and Sorting Algorithms.   }
        \resumeItem{Primarily handled projects, writing autograder tests with dependency checks and extensiviley helping students debug their implementations for projects such as Gitlet(a simplified Git-like VCS).}
        \resumeItem{Maintained and developed course infrastructure. Designed and deployed integration between the course forum and internal tools to provide students with real-time office hours wait times, improving student and staff experience.   }
    \resumeItemListEnd

\resumeSubheading
    {Open Computing Facility}{Berkeley, CA}{DeCal Head Facilitator}{August 2021 - May 2023}
    \resumeItemListStart
            \resumeItem{Taught and developed lab materials for a faculty sponsored, student-run course on Linux System Administration
            , covering topics such as Shell Scripting, Packaging, Networking, Services, Security, Virtualization, Docker and Kubernetes.}
            \resumeItem{Transitioned CI/CD to a Docker-based build process on Jenkins, improving reliability. Implemented Slack notifications for failed builds to enhance development workflow. Automated provisioning and management of 150+ Student VMs using Terraform and Cloud-init.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}

\resumeSubHeadingListStart


    \resumeProjectHeading
    {\textbf{RISC-V CPU}}{}
        \resumeItemListStart
            \resumeItem{Designed and implemented a 3-stage pipelined RISC-V CPU. Wrote comprehensive testbenches and SystemVerilog assertions to rigorously test and debug the 3-stage RISC-V CPU design, ensuring robust functionality and identifying and resolving potential issues.}
            \resumeItem{Added UART based BIOS and MMIO to allow loading in custom programs, including an audio synthesizer with a sigma-delta DAC and a keyboard controlled piano. }
            \resumeItem{Optimized the CPU by implementing data forwarding, branch predictions and achieved a CPI of 1.12. Used Industry Standard tools (Vivado, Synopsys VCS) to identify and optimize the critical path to push the CPU to above 100Mhz.}
            \resumeItem{Winner in the Fall 2023 Apple FPGA Digital Design Competition.}
        \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Pintos - Simple 32-bit OS}}{}
        \resumeItemListStart
            \resumeItem{Implemented additional functionality to an existing OS codebase through the course of a semester.}
            \resumeItem{Added support for multi-threaded user programs by implementing file operation and process control syscalls. Implemented functionality to support subdirectories, extensible files and user files upto 8MiB.}
        \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Secure File Sharing System}}{}
        \resumeItemListStart
            \resumeItem{Designed and implemented a secure file sharing platform assuming that an attacker would have access to a read-only keystore and a read/write datastore. }
            \resumeItem{Included functionality for multiple users, custom access control and efficient appends.}
        \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Hallownest - 3 Node Proxmox Cluster}}{}
    \resumeItemListStart
            \resumeItem{Designed, implemented, and maintained a personal 3 Node Proxmox virtualization cluster using repurposed hardware and open-source solutions. Hosts a variety of services for classes I've taught, friends, myself and the general web.}
            \resumeItem{Configured High Availability(HA) and integrated Ceph Storage  to establish a fault-tolerant and highly available infrastructure, ensuring minimal downtime and robust reliability. }
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------SKILLS-----------
\section{Skills}

\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{Languages}: Python, Java, C, Verilog, SQL, Go, JavaScript, TypeScript, OCaml, LaTeX, Assembly, Lisp, HTML/CSS}{}
    \resumeProjectHeading
    {\textbf{Tools \& Frameworks}: Git, Synopsys VCS, iVerilog, AWS, GCP, Unix, Linux, Docker, Heroku, MongoDB, InfluxDB, \\ React, Vue, Express, Flask, Django, pandas, NumPy, PyTorch, MatPlot, Maven}{}
\resumeSubHeadingListEnd

\end{document}
